CTest Integration of Sikuli Automated GUI Testing

### 2011-06-10 Documentation/Article.tex
Revert "Saved article.tex"
This reverts commit 01adb368dcb53845fd34cb6650e8845e402055e8.
Create Images directory
Updated graphic captions
Added explanation of simple example

\begin{figure}[htp]
 \centering
 \caption{here is my caption}
 \label{fig:SimpleExample}
\end{figure}

@@

% ------------------------------------------------------------------------
\section{Conclusion}

>>>>

Figure 1 shows the Sikuli-IDE for version 0.10.2.  On the left-hand side menu is a list
of commonly used Sikuli commands like find(), click(), and type().  The picture of
the camera within the parentheses indicates the screenshot input variable.  Clicking
on any of these menu functions will automatically set up the Sikuli screen shot mode, whereby
the Sikuli-IDE disappears and what is on the screen at that moment is available to capture 
by selecting a rectangular region of interest.  The function will then appear in the scripting domain
with the snap shot in parentheses as shown in Figure 1.  The user may also type in the function
and invoke the screen shot mode by clicking on the camera in the top menu or by using a
keyboard shortcut. The simple Sikuli script example in Figure 1 will open gedit Text Editor, type a message,
and save the file. (see Figure~\ref{fig:SimpleExample}).

\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/SimpleSikuliExample.png}
 % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
 \caption{Simple Sikuli Script Example in Sikuli-IDE}
 \label{fig:SimpleExample}
\end{figure}

@@

Can you add comments in your example, please?

\begin{figure}[htp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/Gofigure2Example.png}
 % Gofigure2Example.png: 667x826 pixel, 72dpi, 23.53x29.14 cm, bb=0 0 667 826
 \caption{Sikuli Script for Gofigure2 GUI Testing}
 \label{fig:Gofigure2Example}
\end{figure}
% ------------------------------------------------------------------------
\section{Conclusion}
